Identification and performance of stock-recruitment functions in state

### 2024-02-13 Ecov_study/recruitment_functions/presentation/SRR_presentation.Rmd
added 4 new slides

@@

>>>>

## Distribution of maximum(absolute value of gradient) (*new slide)
- very few models dropped for this criterion
- reference lines for -6 (solid) and 5,4,3,2 (exponent for power of 10)
```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 'bad.grad.dist_lowestAIC.plot_grad_6_SE_100_beta_fix.png') )
```

## Distribution of SE (*new slide)
- very few models dropped for this criterion
- mostly impacted mean SRR with no Ecov
```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 'bad.se.dist_lowestAIC.plot_grad_6_SE_100_beta_fix.png') )
```

@@

##  Ability to separate sources of process error (*new slide)
- Better performance when $\rho_{R}$ and $\rho_{Ecov}$ are similar
- No effect of Fhist, $\sigma_{R}$ or Ecov form
```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 'process.error.ratio.est.plot_beta_fix.png') )
```

##  Ability to separate sources of process error (*new slide)
- Better performance when $\rho_{R}$ and $\rho_{Ecov}$ are similar
- No effect of Fhist, $\sigma_{R}$ or Ecov form
```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 'process.error.ratio.est.plot.ylim_beta_fix.png') )
```
